---
title: "rGithub User Guide"
author: "Vladimir Obucina <<vlada_3292@hotmail.com>>"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{rGithub User Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

rGithub library is mainly used to communicate with [GitHub REST API](https://docs.github.com/en/rest). Technology used to create this library
is R6 classes. Three main classes are Api, User and Repository. In this vignette
we'll show you all capabilities and usecases. First we load the library and get
environment variables for token, username and repo which will be used to
demonstrate how each class works:

```{r setup}
library(rGithub)
auth_token <- Sys.getenv("AUTH_TOKEN")
username <- Sys.getenv("USERNAME")
repo <- Sys.getenv("repo")
```
One of the options is to create API object, which can be used to get info about
account and also to get repositories for that account. Let's create one:
```{r}
api <- Api$new(token = auth_token, username = username)
api
```

